\documentclass[a4paper,11pt]{article}
% define the title
\author{GW Dean}
\title{Concepts}
\begin{document}
% generates the title
\maketitle
% insert table of contents
\tableofcontents
\section{Philosophy}

On pg.185 of \emph{History}, Marias identifies a "line" that runs through
philosophy for over 2500 that goes through 7 characters: Parmenides, Plato,
Aristotle, Descartes, Leibniz, Kant and Hegel. By understanding what these
thinkers have in common, I'm assuming that we can get to the root of philosophy.


\subsection{Parmenides}
\subsection{Plato}
\subsection{Aristotle}
\subsection{Descartes}
\subsubsection{The Cartesian Problem}
\subsubsection{Man}
\subsubsection{God}
\subsubsection{The World}
\subsubsection{Rationalism and Idealism}
\subsubsection{Malebranche}
\subsubsection{The Religious Thinkers}
\subsection{Leibniz}
\subsubsection{Leibniz' Philosophic Situation}
\subsubsection{Leibniz' Metaphysics}
\subsubsection{Theory of Knowledge}
\subsubsection{Theodicy}
\subsection{Kant}
\subsubsection{Transcendental Idealism}
\subsubsection{The "Critique of Pure Reason"}
\subsubsection{Practical Reason}
\subsubsection{The Interpretations of Kant's Philosophy}
\subsubsection{Theory of Knowledge}
\subsubsection{Being}
\subsubsection{Philosophy}
\subsection{Hegel}
\subsubsection{The Outline of Hegel's Philosophy}

\begin{verbatim}
The true form in which truth exists can only be the scientific
system of truth. To contribute toward making philosophy approximate
the form of science--toward enabling it to shed the name 'love
of knowledge' and be a real knowledge--this is what I propose
to do.
\end{verbatim}


\subsubsection{The "Phenomenology of Spirit"}
\subsubsection{The "Logic"}
\subsubsection{The Philosophy of Nature}
\subsubsection{The Philosophy of the Spirit}
\section{Statistics}
\subsection{Frequentist}
\subsection{Bayesian}

\subsection{Sources}
Aristotle. \emph{Metaphysics}
Hegel. \emph{The Science of Logic}
Maimonides .\emph{The Guide for the Perplexed}
Marias. \emph{The History of Philosophy}
Spinoza. \emph{Ethics}
Putnam. \emph{American Grace}
Kant. \emph{Introduction to Logic}

\end{document}
